Concurrent Programming in Harmony

### 2021-01-20 book/paper.tex
Latest

The bottom right contains a table with the state of each thread.
The thread that is executing is highlighted in green.
Status information for a thread can include:
\begin{itemize}
\item[] \texttt{runnable}: the thread is runnable but not
currently running.  In Harmony, threads are interleaved and so
at most one thread is actually running;
\item[] \texttt{terminated}: the thread has completed all its
instructions;
\item[] \texttt{failed}: the thread has encountered an error,
such as violating an assertion or divide by zero;
\item[] \texttt{blocked}: the thread cannot make progress until
another thread has updated the shared state;
\item[] \texttt{atomic}: the thread is in \emph{atomic} mode,
not allowing other threads to be scheduled.  This is, for example,
the case when an assertion is being checked;
\item[] \texttt{read-only}: the thread is in \emph{read-only} mode,
not able to modify shared state.  Assertions can execute
arbitrary code including methods, but they are not allowed to
modify the shared state.
\end{itemize}

@@

When you load the HTML file, it shows the state after executing
the last instruction.
As mentioned above, you can go to any point in the execution by
clicking on one of the blocks in the time lines.
There are also various handy keyboard shortcuts:
\begin{itemize}
\item \emph{Right arrow}: go to the next instruction;
\item \emph{Left arrow}: go to the previous instruction;
\item \emph{Down arrow}: go to the next step;
\item \emph{Up arrow}: go to the previous step;
\item \emph{Enter (aka Return)}: go to the next line of Harmony code;
\item \emph{0}: go to the initial state.
\end{itemize}

>>>>

The bottom right contains a table with the state of each thread.
The thread that is executing is highlighted in green.
Status information for a thread can include:
\begin{itemize}
\item[] \texttt{runnable}: the thread is runnable but not
currently running.  In Harmony, threads are interleaved and so
at most one thread is actually running;
\item[] \texttt{running}: the thread is currently executing
instructions;
\item[] \texttt{terminated}: the thread has completed all its
instructions;
\item[] \texttt{failed}: the thread has encountered an error,
such as violating an assertion or divide by zero;
\item[] \texttt{blocked}: the thread cannot make progress until
another thread has updated the shared state.  For example, this
occurs when one of the implementers is waiting for the other
to set its \textit{done} flag;
\item[] \texttt{atomic}: the thread is in \emph{atomic} mode,
not allowing other threads to be scheduled.  This is, for example,
the case when an assertion is being checked;
\item[] \texttt{read-only}: the thread is in \emph{read-only} mode,
not able to modify shared state.  Assertions can execute
arbitrary code including methods, but they are not allowed to
modify the shared state.
\end{itemize}

@@

When you load the HTML file, it shows the state after executing
the last instruction.
As mentioned above, you can go to any point in the execution by
clicking on one of the blocks in the time lines.
There are also various handy keyboard shortcuts:
\begin{tabular}{rl}
\emph{Right arrow}: & go to the next instruction; \\
\emph{Left arrow}: & go to the previous instruction; \\
\emph{Down arrow}: & go to the next step; \\
\emph{Up arrow}: & go to the previous step; \\
\emph{Enter (aka Return)}: & go to the next line of Harmony code; \\
\emph{0}: & go to the initial state.
\end{tabular}
